Guarded Recursion in Agda via Sized Types

### 2019-02-07 code-oneclock-paper/latex/paper.tex
gone through the paper

We also need to provide a semantic version of 
%To interpret simple type theory, we also need to give 
the context operations, the simple type formers and the operations on substitutions.
Since their definitions are standard, we do not discuss them in detail.
For each of them, we need to make a case distinction based on the clock context.
For example, the empty variable context \IC{•} is interpreted either as the unit type
or as the terminal presheaf depending on the clock context.
We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
\input{CloTT/TypeFormers/FunctionType}

@@

This work can be extended in several different directions.
Various type theories for guarded recursion in the literature include
dependent types. Currently, there are two disciplines for these two features: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
the syntax and semantics of \GTT\ with dependent types following one
of these methods.

Abel and Vezzosi \cite{AbelV14} formalized a simple type theory
extended with the later modality in Agda. They focus on operational
properties of the calculus and give a certified proof of strong
normalization. As future work, we plan to investigate the metatheory
and the dynamic behavior of \GTT\ by formalizing a  type
checker and a normalization algorithm.

>>>>

We also need to provide a semantic version of 
%To interpret simple type theory, we also need to give 
the context operations, the simple type formers and the operations on substitutions.
Since their definitions are standard, we do not discuss them in detail.
For each of them, we need to make a case distinction based on the clock context.
For example, the empty variable context \IC{•} is interpreted either as the unit type
or as the terminal presheaf, depending on the state of the clock context.
We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
\input{CloTT/TypeFormers/FunctionType}

@@

This work can be extended in several different directions.
Various type theories for guarded recursion in the literature include
dependent types. Currently, there exist two disciplines for mixing
dependent types with guarded recursion: delayed substitutions
\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
the syntax and semantics of \GTT\ with dependent types following one
of these two methods.

Abel and Vezzosi \cite{AbelV14} formalized a simple type theory
extended with the later modality in Agda. They focus on operational
properties of the calculus and give a certified proof of strong
normalization. As future work, we plan to investigate the metatheory
and the dynamic behavior of \GTT\ by formalizing a  type
checker and a normalization algorithm. This would also set up the
basis for a usable implementation of \GTT.
